Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on tables

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
  \begin{tabular}{crrr}
    \toprule
    & \# buckets & \# files & avg. \# files per bucket \\
    \midrule
    \radamsa{} & 82 & 241 & 2.9 \\
    \quickfuzz{} & 38 & 87 & 2.3 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \setlength{\tabcolsep}{5pt}
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.\Fix{falta add test262}}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 30 & 4 & 121 & 3 & 143 \\
    \quickfuzz{} & 12 & 7 & 67 & 8 & 89 \\
    \midrule
    \textbf{total} & \Fix{x} & \Fix{x} & \Fix{x} & \Fix{x} & \Fix{x} \\    
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    and true positives.}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 18 & - \\
    & Timeout/OME & 23 & - \\
    & Not Implemented & 19 & - \\
    & * Invalid Input & 10 & - \\    
    & * Error Message Mismatch & 3 & - \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & - \\
    & Bug & - \\
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
  \begin{tabular}{crrr}
    \toprule
    & \# buckets & \# files & avg. \# files per bucket \\
    \midrule
    \radamsa{} & 82 & 319 & 3.8 \\
    \quickfuzz{} & 78 & 218 & 2.7 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \setlength{\tabcolsep}{5pt}
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 137 & 47 & 323 & 21 & 483 \\
    \quickfuzz{} & 81 & 62 & 649 & 13 & 369 \\
    \midrule
    \textbf{total} & 218 &  & 972 & 34 & 852 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    and true positives.}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 26 & - \\
    & Timeout/OME & 23 &  \\
    & * Invalid Input & 10 & - \\    
    & * Error Message Mismatch & 3 & - \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & - \\
    & Bug & - \\
    \bottomrule     
  \end{tabular}
\end{table}
